---
title: "Staff testing scenarios"
author: "Chris Hoover et al"
date: "4/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)

library(tidyverse)
source(here::here("R/Utils.R"))
source(here::here("R/Sim_Functions.R"))
```

## Individual-based simulation framework  
* All staff are assigned a work schedule that determines time frames when they are working. $\mathbf{I}(w_{it})$ is an indicator function for whether staff member $i$ is working at the facility on day $t$.  
* In addition to their work schedule, all staff are assigned a testing schedule, encoded by function $\mathbf{T}(w_{it})$.  
* All staff are subject to two sources of infection: community and workplace, represented by force of infection parameters $\lambda_c$ and $\lambda_w$, respectively. In addition, we introduce a partitioning parameter, $\alpha$, representing the relative probability of acquiring infection in the workplace versus in the community, therefore $\lambda_w=\lambda_c\alpha$ and $\Lambda_{it}=\lambda_c\alpha\mathbf{I}(w_{it})+\lambda_c(1-\mathbf{I}(w_{it}))$. New cases at each time step are then generated by subjecting all susceptible staff to a Bernoulli trial where $p=\Lambda_{it}$  
* Whenever a new staff infection is generated, parameters for the individual are drawn to determine the latent period ($t_{latent}$), the incubation period ($t_{incubation}$), the total infectious period ($t_{infectious}$), and whether the case will be asymptomatic or symptomatic ($p_{symp}$) to generate an infectiousness profile ($\beta_{it}$). Assuming constant $\mathcal{R}$ across all individuals, the expected number of workplace cases produced on day $t$ by individual $i$ is $r_{it}=\mathcal{R}\beta_{it}\mathbf{I}(w_{it})$  
* Main outcome is expected number of cases transmitted by staff over the simulation timeframe: $\mathbf{E}[cases]=\sum_{t=1}^{t_{sim}}\sum_{i=1}^n\mathbf{I}(w_{it})r_{it}$   

## Individual based model simulations  
### Goal 1: Determine impact of different testing interventions on expected number of imported cases  
* **S1)** No testing  
* **S2)** Self isolation at symptom onset  
  - SA: proportion of symptomatic cases that adhere to self-isolation  
* **S3)** Random PCR testing once per work week with test report on second day following test  
* **S4)** Random antigen testing once per work week with immediate test report  
* **S5)** PCR testing on first day of work week with test report on second day following test  
* **S6)** Antigen testing on first day of work week with immediate test report  
* **S7)** Random PCR testing twice per work week with test report on second day following test  
* **S8)** Random antigen testing twice per work week with immediate test report  
* **S9)** PCR testing on first and third day of work week with test report on second day following test  
* **S10)** Antigen testing on first and third day of work week with immediate test report  

**Proposed table**: number of cases avoided per test conducted relative to no testing scenario for each strategy above  

### Goal 2: Determine optimal antigen-based testing strategy across workplace vs community driven transmission scenarios  




```{r sim_setup, echo = FALSE}
# Sim inputs
  n_sims      <- 100
  lambda      <- 0.005
  days        <- 180
  dt          <- 8/24
  sim_t       <- days*(1/dt)
  exp_cases   <- numeric(length = sim_t)
  n_staff     <- 700
  staff_state <- rep("S", n_staff)

# Generate master schedule
  work_weeks         <- ceiling(days/7)
  schedule_shifts    <- rep(c("M", "E", "N"), times = days)
  schedule_days      <- rep(rep(c("U", "M", "T", "W", "R", "F", "S"), each = 1/dt), 
                         times = work_weeks)[1:length(schedule_shifts)]
  schedule_work_week <- rep(1:work_weeks, each = 7/dt)[1:length(schedule_shifts)]
  master_schedule    <- paste(schedule_days, schedule_shifts, schedule_work_week, sep = "_")

```

```{r base_workers, echo = FALSE}
set.seed(430)
# Generate list of workers with no testing for model simulation
workers <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule  
  test_schedule <- rep(0, sim_t)
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})
```

```{r workers_testdays, echo = FALSE}
set.seed(430)
# Generate list of workers with testing on first day of shift for model simulation
workers_testday1 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  test_schedule <- if_else(substr(work_days,1,1) == schedule_days & work_shift == schedule_shifts,
                           1, 0 )
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

workers_testday2 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  test_schedule <- if_else(substr(work_days,2,2) == schedule_days & work_shift == schedule_shifts,
                           1, 0 )
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

workers_testday3 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  test_schedule <- if_else(substr(work_days,3,3) == schedule_days & work_shift == schedule_shifts,
                           1, 0 )
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

workers_testday4 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  test_schedule <- if_else(substr(work_days,4,4) == schedule_days & work_shift == schedule_shifts,
                           1, 0 )
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

workers_testday13 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  test_schedule <- if_else(substr(work_days,1,1) == schedule_days & work_shift == schedule_shifts, 1, 
                           if_else(substr(work_days,3,3) == schedule_days & work_shift == schedule_shifts, 1, 0))
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

workers_testday24 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  test_schedule <- if_else(substr(work_days,2,2) == schedule_days & work_shift == schedule_shifts, 1, 
                           if_else(substr(work_days,4,4) == schedule_days & work_shift == schedule_shifts, 1, 0))
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

# Random work days
# Single random day during the work week
workers_testday_r1 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaul probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  work_days_string <- sapply(1:nchar(work_days), function(x){substr(work_days,x,x)})
  
  test_days <- sample(work_days_string, work_weeks, replace = T)
  test_days_schedule <- paste(test_days, work_shift, c(1:work_weeks), sep = "_")
  
  test_schedule <- if_else(master_schedule %in% test_days_schedule, 1, 0)
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

# Two random days during the work week
workers_testday_r2 <- lapply(1:n_staff, function(s){
  # Worker state and infectious profile parameters for if/when they become infected  
  state <- "S"
  t_inc <- rlnorm(1, 1.63,0.5)
  t_lnt <- t_inc + runif(1, -2.5, 0)
  t_inf <- t_lnt + runif(1, 6.5, 9.5)
  
  # Worker schedule  
  # Randomly determine if worker works morning, night or day shift with equal probability  
  draw_shift <- runif(1,0,1)
  work_shift <- if_else(draw_shift < 1/3, "M",
                        if_else(draw_shift > 2/3, "N", "E"))
  
  # Randomly determine weekly schedule from four options: 1)Sat-Tues, 2)Tues-Sat,3)Thurs-Sun, 4)Mon-Thurs with eaual probability
  draw_days <- runif(1,0,1)
  work_days <- if_else(draw_days < 1/4, "SUMT",
                       if_else(draw_days > 3/4, "MTWR", 
                               if_else(draw_days > 1/4 & draw_days < 2/4, "TWRF", "RFSU")))
  
  # Binary work schedule
  shift10 <- if_else(work_shift == schedule_shifts, 1, 0)
  work10  <- if_else(schedule_days %in% unlist(strsplit(work_days, "")), 1, 0)
  
  schedule_fin <- if_else(shift10 + work10 == 2, 1, 0)
  
  # Binary test schedule with test occurring on day 1 of work shift
  work_days_string <- sapply(1:nchar(work_days), function(x){substr(work_days,x,x)})
  
  test_days <- lapply(1:work_weeks, function(x){sample(work_days_string, 2, replace = F)})
  test_days_schedule <- paste(test_days, work_shift, rep(c(1:work_weeks), each = 2), sep = "_")
  
  test_schedule <- if_else(master_schedule %in% test_days_schedule, 1, 0)
  
  # Return worker characteristics in list  
  worker                <- list()
  worker$state          <- state
  worker$t_latent       <- t_lnt
  worker$t_incubation   <- t_inc
  worker$t_infectious   <- t_inf
  worker$infectiousness <- numeric()
  worker$t_infect       <- -Inf
  worker$work_schedule  <- schedule_fin
  worker$test_schedule  <- test_schedule
  
  return(worker)
  
})

```

## No workplace transmission ($\alpha=0$) scenarios  
```{r run_sims_alpha0, echo = FALSE, cache = TRUE}
# No testing  
no_test_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 0,
                        workers = workers,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = "None",
           testday = "None",
           testfreq = "None")
}))

# Random pcr testing once per week
test_r1_pcr_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 2/dt-1,
                        workers = workers_testday_r1,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 2,
           testday = "rand",
           testfreq = 1)
}))


# Random antigen testing once per week
test_r1_ant_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 0,
                        workers = workers_testday_r1,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 0,
           testday = "rand",
           testfreq = 1)
}))

# pcr testing on first day of work week
test_day1_pcr_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 2/dt-1,
                        workers = workers_testday1,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 2,
           testday = "1",
           testfreq = 1)
}))


# antigen testing on first day of work week
test_day1_ant_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 0,
                        workers = workers_testday1,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 0,
           testday = "1",
           testfreq = 1)
}))


# Random pcr testing twice per week
test_r2_pcr_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 2/dt-1,
                        workers = workers_testday_r2,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 2,
           testday = "rand",
           testfreq = 2)
}))


# Random antigen testing twice per week
test_r2_ant_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 0,
                        workers = workers_testday_r2,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 0,
           testday = "rand",
           testfreq = 2)
}))


# pcr testing on first and third day of work week
test_day13_pcr_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 2/dt-1,
                        workers = workers_testday13,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 2,
           testday = "13",
           testfreq = 2)
}))


# antigen testing on first and third day of work week
test_day13_ant_sims_a0 <- bind_rows(lapply(1:n_sims, function(x){
  sim_work_transmission(Lambda  = 0.01,
                        alpha   = 0,
                        R       = 1,
                        delay   = 0,
                        workers = workers_testday13,
                        sim_t   = sim_t,
                        dt      = dt,
                        verbose = F) %>% 
    mutate(sim = x,
           alpha = 0,
           delay = 0,
           testday = "13",
           testfreq = 2)
}))


```

